---
title: "Affordability Comparisons for Municipalities and Water Systems"
author: "NJDEP Office of Economic Analysis"
date: "1/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("./Poverty_Measures_Calculations.R")
```



## Methodology

### Clean Water Affordability Criteria

Source: https://www.nj.gov/dep/dwq/pdf/NJWB_FFY21-SFY22_CW_Final_IUP_FinalAmendments.pdf#page=24

Text from page 32: 

Section 603(i)(2) of WRRDA requires States to develop affordability criteria that will assist in identifying
applicants that would have difficulty financing projects without additional subsidization. The law requires
that states establish affordability criteria by September 30, 2015, after providing notice and an opportunity
for public comment, which is being accomplished through this new feature of NJ’s CW Intended Use Plan.

Section 603(i)(2)(A) of WRRDA requires that states base their criteria on:

*  income;
*  unemployment data;
*  population trends; and
*  other data determined relevant by the State.

In New Jersey, those applicants where the following income, unemployment data, and population trends
exist, based upon the sources below for each factor, are considered to have satisfied the State’s CWSRF
affordability criteria:

* Median household income of $90,000 or less;
* County-wide unemployment of 5% or higher; and
* Population trend of 2% or lower.

Applicants that do not meet the specifications above do not meet the State’s CWSRF Affordability Criteria


## Full Table


```{r full_table, echo=FALSE}
knitr::kable(
  head(Poverty_Data_Final[, 1:10], 10), "simple",
  caption = 'test'
)
```

```{r clean_table, echo=FALSE}
kbl()